Machine Learning Autoencoder Applied to Communication Channels

### 2019-06-07 Rapport/Article/Article.tex
Seance 06/07/2019

\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{verbatim}

@@

Then, the objective of the receiver is to estimate the original message with an empirical error probability, or a BER, defined as

@@

@@

Whilst autoencoders are more complex dimensional wise compared to NN decoders, the readily access to graphical processing units (GPUs) contributed to the feasibility of this technique, tackling the \textit{curse of dimensionality} challenge in ML. This type of hardware made possible the approach of the layer-by-layer supervised training by stochastic gradient descent optimization applied in this work. \cite{GPU}.

@@

\section{Implementation and Methodology}
This section explains the main implementation procedures in order to replicate the results and understand in depth the methodology behind the work. For organizational purposes, the section is divided into two subsections, where the first concerns the experiments relating to the ML based decoders and the second treats the implementation of the ML based autoencoders.

@@

\begin{figure}[!ht]
  \centering
    \includegraphics[width=0.5\textwidth]{images/MAP_MLNN1H_p_0}
    \caption{Test caption to test image.}\label{fig:1HD}
\end{figure}

>>>>

%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{verbatim}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother

@@

The objective of the receiver is to estimate the original message. The empirical error probability, or a BER, in this process is defined as

@@

The Hamming distance $d_H:\mathcal{X}\mapsto \mathbb{Z}$ is a metric in the word subset which in the context of linear coding is equal to equation \ref{eq:dh}. Noteworthy for the MAP rule, a non zero Hamming distance indicates that there is a block error, and ultimately at least a binary error in the received code word.
\begin{equation}\label{eq:dh}
d_H(\textbf{x},\textbf{y}) = \sum_{i=1}^{n} y_i \text{ XOR } x_i 
\end{equation}

@@

Whilst autoencoders are more complex dimensional wise compared to NN decoders, the readily access to graphical processing units (GPUs) contributed to the feasibility of this technique, tackling the \textit{curse of dimensionality} challenge in ML. This type of hardware made possible the approach of the layer-by-layer supervised training by stochastic gradient descent optimization applied in this work. \cite{GPU}

@@

\section{Implementation and Methodology}
This section explains the main implementation procedures in order to replicate the results and understand in depth the methodology behind the work. For organizational purposes, the section is divided into three subsections. First, the MAP algorithm for a linear code is shown, then the experiments relating to the ML based decoders are assessed and finally the implementation of the ML based autoencoder is explained.

\subsection{MAP Rule}

The pseudo code of the MAP decoder algorithm is available below.

\begin{algorithm}
\caption{MAP rule for BSC and linear block code.}\label{euclid}
\hspace*{\algorithmicindent} \textbf{Input:} received block $\textbf{y}^n \in \{0,1\}^n$, the code word set $\mathcal{X}$ and generator matrix $G_{k \times n}$. \\
\hspace*{\algorithmicindent} \textbf{Output:} message estimation $\hat{\textbf{u}}^k \in \{0,1\}^k$.
\begin{algorithmic}[H]
\Procedure{MAP Decoder}{$y,\mathcal{X}, G$}
\State $\textit{p} \gets \text{channel crossover probability}$
\For{i in \textit{range}($2^k$)}
\State $\text{distances}[i] \gets d_H(\textbf{y},word[i] \in \mathcal{X})$
\EndFor
\State $\hat{\textbf{x}} \gets argmin(\text{distances})$
\State $\hat{\textbf{u}} $
\Return $\hat{\textbf{u}}$
\EndProcedure
\end{algorithmic}
\end{algorithm}

\begin{figure}[!ht]
  \centering
    \includegraphics[width=0.5\textwidth]{images/20190607-160812_MAP}
    \caption{MAP algorithm performance in terms of BER versus channel crossover probability.}\label{fig:MAP}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
    \includegraphics[width=0.5\textwidth]{images/MAP_MLNN1H_p_0}
    \caption{One hot decoding BER performance. NN decoder trained with a channel crossover probability error of $p_t=0$.}\label{fig:1HD}
\end{figure}

\begin{figure}[!ht]
  \centering
    \includegraphics[width=0.5\textwidth]{images/20190529-142119_MAP_MLNN_Mep_65536}
    \caption{Array decoding BER performance. NN trained with a channel crossover probability error of $p_t=0.07$.}\label{fig:ArrayD}
\end{figure}
